---
title: "R Notebook"
output: html_notebook
---
################################################
##
################################################
```{r}
#' Computes the reinforcement learning policy
#'
#' Computes reinforcement learning policy from a given state-action table Q.
#' The policy is the decision-making function of the agent and defines the learning
#' agent's behavior at a given time.
#'
#' @param x Variable which encodes the behavior of the agent. This can be
#' either a \code{matrix}, \code{data.frame} or an \code{\link{rl}} object.
#' @seealso \code{\link{ReinforcementLearning}}
#' @return Returns the learned policy.
#' @examples
#' # Create exemplary state-action table (Q) with 2 actions and 3 states
#' Q <- data.frame("up" = c(-1, 0, 1), "down" = c(-1, 1, 0))
#'
#' # Show best possible action in each state
#' computePolicy(Q)
#'
#' @rdname computePolicy
#' @export
computePolicy <- function(x) {
  UseMethod("computePolicy", x)
}

#' @export
computePolicy.matrix <- function(x) {
  policy <- colnames(x)[apply(x, 1, which.max)]
  names(policy) <- rownames(x)
  return(policy)
}

#' @export
computePolicy.data.frame <- function(x) {
  return(computePolicy(as.matrix(x)))
}

#' @export
computePolicy.rl <- function(x) {
  return(computePolicy(x$Q))
}

#' @export
computePolicy.default <- function(x) {
  stop("Argument invalid.")
}

#' Computes the reinforcement learning policy
#'
#' Deprecated. Please use [ReinforcementLearning::computePolicy()] instead.
#'
#' @param x Variable which encodes the behavior of the agent. This can be
#' either a \code{matrix}, \code{data.frame} or an \code{\link{rl}} object.
#' @seealso \code{\link{ReinforcementLearning}}
#' @return Returns the learned policy.
#' @rdname policy
#' @export
policy <- function(x) {
  .Deprecated("computePolicy")
  computePolicy(x)
}

```
################################################
## This function contains all of the parameters 
## in one location so that it is easy to update 
## the model as needed       
################################################

```{r}
LoadParameters<-function()
{
  parameters = data.frame(matrix(vector(), 1, 16, dimnames=list(c(), c("seed", "cols","rows","percpop","biasYN","bias","percgroup","vulnamount",      "daylength","traveltime","detaintime","alpha","gamma","epsilon","pop","popdensity"))),stringsAsFactors=F)
  parameters$seed=7013         # Seed 
  parameters$bias=.1          # Amount Bias
  parameters$percGroup=.4     # Percentage of Biased Group
  parameters$indirect1=.4
  parameters$indirect2=.6
  #parameters$vulnamount=.05    # Vulnerability
  #parameters$perccrim=.1      # Possibly Increase in Criminal due to Vulnerability  
  #parameters$percsusp=.25    # Possibly Increase in Suspicious due to Vulnerability
  parameters$daylength=28     # Length of Day
  parameters$traveltime=1     # Travel Time
  parameters$detaintime=4      # Detain Time
  parameters$alpha = .6       # Learning Rate [0,1]
  parameters$gamma = .8       # Thoughtfulness Factor [0,1]
  parameters$epsilon = .3     # Exploration Parameter [0,1]
  parameters$MoveReward=0
  parameters$numtrain=3 # Number Train runs
  parameters$numtest=3 # Number of Test runs
  parameters$itertrain=3 #Number Train Iterations
  #Parameters$pop=Parameters$rows*Parameters$cols     # Total Population: pop
  parameters$pop=999

return(parameters)
}
```
################################################
##This creates the set of choices
################################################
```{r}
createsamplefunction<-function(population, parameters) 
  {

  id_num0<-sample(1:nrow(population), parameters$daylength*2, replace=F)
  Left<-NA
  Right<-NA
  LeftReward<-NA
  RightReward<-NA
  LeftCrim<-NA
  RightCrim<-NA
  LeftGroup<-NA
  RightGroup<-NA
  LeftSusp<-NA
  RightSusp<-NA
  LeftSuspCode<-NA
  RightSuspCode<-NA
  LeftDirectCode<-NA
  RightDirectCode<-NA
  LeftIndirectCode<-NA
  RightIndirectCode<-NA
  LeftRandomCode<-NA
  RightRandomCode<-NA  
  LeftCrimCode<-NA
  RightCrimCode<-NA
  NextSuspState<-NA 
  NextDirectState<-NA
  NextIndirectState<-NA
  NextCrimState<-NA
  SuspState<-NA 
  DirectState<-NA
  IndirectState<-NA
  CrimState<-NA
  State<-NA
  NextState<-NA
  RandomState<-NA
  NextRandomState<-NA
  for(ii in 1: parameters$daylength)
  {
    id_num1<-id_num0[ii]
    id_num2<-id_num0[ii+parameters$daylength]
    Left[ii]<-id_num1
    Right[ii]<-id_num2
    LeftReward[ii]<-population$Reward[id_num1]
    RightReward[ii]<-population$Reward[id_num2]
    LeftGroup[ii]<-population$Group[id_num1]
    RightGroup[ii]<-population$Group[id_num2]
    LeftSusp[ii]<-population$Susp[id_num1]
    RightSusp[ii]<-population$Susp[id_num2]
    LeftCrim[ii]<-population$Crim[id_num1]
    RightCrim[ii]<-population$Crim[id_num2]
    State[ii]<-NA
    LeftSuspCode[ii]<-population$Susp[id_num1]
    RightSuspCode[ii]<-population$Susp[id_num2]
    LeftDirectCode[ii]<-population$DirectCode[id_num1]
    RightDirectCode[ii]<-population$DirectCode[id_num2]
    LeftIndirectCode[ii]<-population$IndirectCode[id_num1]
    RightIndirectCode[ii]<-population$IndirectCode[id_num2]
    LeftCrimCode[ii]<-population$Crim[id_num1]
    RightCrimCode[ii]<-population$Crim[id_num2]
    LeftRandomCode[ii]<-sample(0:9,1)
    RightRandomCode[ii]<-sample(0:9,1)
    SuspState[ii]<-paste0(LeftSuspCode[ii],'.',RightSuspCode[ii])
    DirectState[ii]<-paste0(LeftDirectCode[ii],'.',RightDirectCode[ii])
    IndirectState[ii]<-paste0(LeftIndirectCode[ii],'.',RightIndirectCode[ii])
    CrimState[ii]<-paste0(LeftCrimCode[ii],'.',RightCrimCode[ii])
    RandomState[ii]<-paste0(LeftRandomCode[ii],'.',RightRandomCode[ii])    
    NextSuspState[ii-1]<-paste0(LeftSuspCode[ii],'.',RightSuspCode[ii])
    NextSuspState[ii]<-"End" 
    NextDirectState[ii-1]<-paste0(LeftDirectCode[ii],'.',RightDirectCode[ii])
    NextDirectState[ii]<-"End"
    NextIndirectState[ii-1]<-paste0(LeftIndirectCode[ii],'.',RightIndirectCode[ii])
    NextIndirectState[ii]<-"End"
    NextCrimState[ii-1]<-paste0(LeftCrimCode[ii],'.',RightCrimCode[ii])
    NextCrimState[ii]<-"End"
    NextRandomState[ii-1]<-paste0(LeftRandomCode[ii],'.',RightRandomCode[ii])
    NextRandomState[ii]<-"End"  
    }
createRLsample<-data.frame(Left,LeftGroup, LeftSusp,LeftSuspCode,LeftDirectCode,LeftIndirectCode, LeftCrim, LeftRandomCode, LeftReward, Right, RightGroup, RightSusp, RightSuspCode,   RightDirectCode, RightIndirectCode, RightCrim,RightRandomCode, RightReward,SuspState, DirectState, IndirectState,CrimState,RandomState, NextSuspState, NextDirectState, NextIndirectState,NextCrimState, NextRandomState)
return(createRLsample)
}
```
################################################
##Create the state diagram
################################################
```{r}
statediagramfunction <- function(createsample, parameters,flag) {
time = parameters$daylength
detain = parameters$detaintime
move = parameters$traveltime

statemap<-data.frame("State"=paste0(time,".",createsample$State[1]), 
                    "Action"="Left", 
                    "Reward"=createsample$LeftReward[1], 
                    "NextState"=paste0(time-detain,".",createsample$NextState[1]),
                    "LeftGroup"=createsample$LeftGroup[1],
                    "LeftSusp"=createsample$LeftSusp[1],
                    "LeftCrim"=createsample$LeftCrim[1],
                    "LeftRandom"=createsample$LeftRandomCode[1],                    
                    "LeftReward"=createsample$LeftReward[1],
                    "RightGroup"=createsample$RightGroup[1],
                    "RightSusp"=createsample$RightSusp[1],                 
                    "RightCrim"=createsample$RightCrim[1],
                    "RightRandom"=createsample$RightRandomCode[1],
                    "RightReward"=createsample$RightReward[1])
                    nextrow<-data.frame("State"=paste0(time,".",createsample$State[1]), 
                    "Action"="Right", 
                    "Reward"=createsample$RightReward[1], 
                    "NextState"=paste0(time-detain,".",createsample$NextState[1]),
                    "LeftGroup"=createsample$LeftGroup[1],
                    "LeftSusp"=createsample$LeftSusp[1],
                    "LeftCrim"=createsample$LeftCrim[1],
                    "LeftRandom"=createsample$LeftRandom[1],
                    "LeftReward"=createsample$LeftReward[1],
                    "RightGroup"=createsample$RightGroup[1],
                    "RightSusp"=createsample$RightSusp[1],                 
                    "RightCrim"=createsample$RightCrim[1],
                    "RightRandom"=createsample$RightRandom[1],
                    "RightReward"=createsample$RightReward[1])
                    statemap<-rbind(statemap,nextrow)
                    
                    nextrow<-data.frame("State"=paste0(time,".",createsample$State[1]), 
                    "Action"="None", 
                    "Reward"=0, 
                    "NextState"=paste0(time-move,".",createsample$NextState[1]),
                    "LeftGroup"=createsample$LeftGroup[1],
                    "LeftSusp"=createsample$LeftSusp[1],
                    "LeftCrim"=createsample$LeftCrim[1],
                    "LeftRandom"=createsample$LeftRandom[1],
                    "LeftReward"=createsample$LeftReward[1],
                    "RightGroup"=createsample$RightGroup[1],
                    "RightSusp"=createsample$RightSusp[1],                 
                    "RightCrim"=createsample$RightCrim[1],
                    "RightRandom"=createsample$RightRandom[1],
                    "RightReward"=createsample$RightReward[1])
                    statemap<-rbind(statemap,nextrow)

for(ii in 1:1000)
{
  statedummy<-as.character(statemap$NextState[ii])
  flag<-0
  if (is.na(statedummy))
  {}
  else if (statedummy=="End")
  {}
  else
  {
    for(jj in 1:nrow(statemap))
    {
      if (statedummy==statemap$State[jj])  
      {
        flag<-1
      }
    }
  if(flag==0)
  {
    openstate<-unlist(stri_split_fixed(as.character(statedummy),".", fixed = TRUE, n=2))
    for (kk in 1:nrow(createsample))
    {
      if (openstate[2]==as.character(createsample$State[kk]))
      {
        timedet<-as.numeric(openstate[1])-detain
        timemove<-as.numeric(openstate[1])-move
        if(as.numeric(openstate[1])>=detain)
          {
          nextrow<-data.frame("State"=statedummy, 
                                "Action"="Left", 
                                "Reward"=createsample$LeftReward[kk], 
                                "NextState"=paste0(timedet,".",createsample$State[kk+1]),
                                "LeftGroup"=createsample$LeftGroup[kk],
                                "LeftSusp"=createsample$LeftSusp[kk],
                                "LeftCrim"=createsample$LeftCrim[kk],
                                "LeftRandom"=createsample$LeftRandomCode[kk],
                                "LeftReward"=createsample$LeftReward[kk],
                                "RightGroup"=createsample$RightGroup[kk],
                                "RightSusp"=createsample$RightSusp[kk],                 
                                "RightCrim"=createsample$RightCrim[kk],
                                "RightRandom"=createsample$RightRandomCode[kk],
                                "RightReward"=createsample$RightReward[kk])
        nextrow2<-data.frame("State"=statedummy, 
                                "Action"="Right", 
                                "Reward"=createsample$RightReward[kk], 
                                "NextState"=paste0(timedet,".",createsample$State[kk+1]),
                                "LeftGroup"=createsample$LeftGroup[kk],
                                "LeftSusp"=createsample$LeftSusp[kk],
                                "LeftCrim"=createsample$LeftCrim[kk],
                                "LeftRandom"=createsample$LeftRandomCode[kk],
                                "LeftReward"=createsample$LeftReward[kk],
                                "RightGroup"=createsample$RightGroup[kk],
                                "RightSusp"=createsample$RightSusp[kk],                 
                                "RightCrim"=createsample$RightCrim[kk],
                                "RightRandom"=createsample$RightRandomCode[kk],
                                "RightReward"=createsample$RightReward[kk])
          } 
        else if(as.numeric(openstate[1])<detain)
        {
          nextrow<-data.frame("State"=statedummy, 
                                "Action"="Left", 
                                "Reward"=-50, 
                                "NextState"="End",
                                "LeftGroup"=createsample$LeftGroup[kk],
                                "LeftSusp"=createsample$LeftSusp[kk],
                                "LeftCrim"=createsample$LeftCrim[kk],
                                "LeftRandom"=createsample$LeftRandomCode[kk],           
                                "LeftReward"=createsample$LeftReward[kk],
                                "RightGroup"=createsample$RightGroup[kk],
                                "RightSusp"=createsample$RightSusp[kk],                 
                                "RightCrim"=createsample$RightCrim[kk],
                                "RightRandom"=createsample$RightRandomCode[kk],
                                "RightReward"=createsample$RightReward[kk])
          nextrow2<-data.frame("State"=statedummy, 
                                "Action"="Right", 
                                "Reward"=-50, 
                                "NextState"="End",
                                "LeftGroup"=createsample$LeftGroup[kk],
                                "LeftSusp"=createsample$LeftSusp[kk],
                                "LeftCrim"=createsample$LeftCrim[kk],
                                "LeftRandom"=createsample$LeftRandomCode[kk],
                                "LeftReward"=createsample$LeftReward[kk],
                                "RightGroup"=createsample$RightGroup[kk],
                                "RightSusp"=createsample$RightSusp[kk],                 
                                "RightCrim"=createsample$RightCrim[kk],
                                "RightRandom"=createsample$RightRandomCode[kk],
                                "RightReward"=createsample$RightReward[kk])
          } 
        if(as.numeric(openstate[1])>=move)
        {
        nextrow3<-data.frame("State"=statedummy, 
                            "Action"="None", 
                            "Reward"=0, 
                            "NextState"=paste0(timemove,".",createsample$State[kk+1]),
                            "LeftGroup"=createsample$LeftGroup[kk],
                            "LeftSusp"=createsample$LeftSusp[kk],
                            "LeftCrim"=createsample$LeftCrim[kk],
                            "LeftRandom"=createsample$LeftRandomCode[kk],
                            "LeftReward"=createsample$LeftReward[kk],
                            "RightGroup"=createsample$RightGroup[kk],
                            "RightSusp"=createsample$RightSusp[kk],                 
                            "RightCrim"=createsample$RightCrim[kk],
                            "RightRandom"=createsample$RightRandomCode[kk],
                            "RightReward"=createsample$RightReward[kk])
        statemap<-rbind(statemap, nextrow, nextrow2, nextrow3)
        }
        else if (as.numeric(openstate[1])<move)
        {
          nextrow3<-data.frame("State"=statedummy, 
                            "Action"="None", 
                            "Reward"=0, 
                            "NextState"="End",
                            "LeftGroup"=createsample$LeftGroup[kk],
                            "LeftSusp"=createsample$LeftSusp[kk],
                            "LeftCrim"=createsample$LeftCrim[kk],
                            "LeftRandom"=createsample$LeftRandomCode[kk],
                            "LeftReward"=createsample$LeftReward[kk],
                            "RightGroup"=createsample$RightGroup[kk],
                            "RightSusp"=createsample$RightSusp[kk],                 
                            "RightCrim"=createsample$RightCrim[kk],
                            "RightRandom"=createsample$RightRandomCode[kk],
                            "RightReward"=createsample$RightReward[kk])
                            statemap<-rbind(statemap, nextrow, nextrow2, nextrow3)
          }
        } 
      }
    }
  }
}
return(statemap)
}
```
################################################
## Call RL with an existing model
################################################
```{r}
runRL<-function(RLdat, trainmodelold, parameters)
{
# Load dataset
RLdat$State<-as.character(RLdat$State)
RLdat$NextState<-as.character(RLdat$NextState)
RLdat$Action<-as.character(RLdat$Action)
# Define reinforcement learning parameters
control <- list(alpha = parameters$alpha, gamma = parameters$gamma, epsilon = parameters$epsilon)
# Perform reinforcement learning
trainmodelnew <- ReinforcementLearning(RLdat, s = "State", a = "Action", r = 
                                 "Reward", 
                               s_new = "NextState", iter = parameters$itertrain, control = control, model=trainmodelold)
# Print optimal policy
return(trainmodelnew)
}

```
################################################
## This is the initial reinforcement learning 
## routine. Calls RL without an existing model
################################################


```{r}
runRLinit<-function(RLdat,parameters)
{
# Load dataset
RLdat$State<-as.character(RLdat$State)
RLdat$NextState<-as.character(RLdat$NextState)
RLdat$Action<-as.character(RLdat$Action)
# Define reinforcement learning parameters
control <- list(alpha = parameters$alpha, gamma = parameters$gamma, epsilon = parameters$epsilon)

# Perform reinforcement learning
trainmodelnew <- ReinforcementLearning(RLdat, s = "State", a = "Action", r = 
                                 "Reward", 
                               s_new = "NextState", iter = parameters$itertrain, control = control)
# Print optimal policy
return(trainmodelnew)
}

```

################################################
## This is the population seeding routine.
################################################

```{r}

createpopulation<-function(parameters)
{
set.seed=(parameters$seed)

population = data.frame(matrix(vector(), 0, 8, dimnames=list(c(), c("ID", "Group", "Crim", "Indirect","Reward", "Susp", "DirectCode", "IndirectCode"))),stringsAsFactors=F)
person = data.frame(matrix(vector(), 1, 8, dimnames=list(c(), c("ID", "Group", "Crim", "Indirect","Reward", "Susp", "DirectCode", "IndirectCode"))),stringsAsFactors=F)

for (ii in 1:parameters$pop)
{
person$ID <-sprintf("%03d",ii)
person$Group <- sample(1:2, 1, replace=T,prob=c(1-parameters$percGroup,parameters$percGroup))
person$Crim<- sample(1:4, 1, replace=T)
person$Reward=person$Crim
if (person$Group==1)
{
  person$Indirect<- sample(0:1, 1, replace=T,prob=c(1-parameters$indirect1,parameters$indirect1))
  person$Susp<-  round(person$Crim +   rnorm(1,0,1))
  if(person$Susp<0)
  {person$Susp<-0}
}
if (person$Group==2)
{
  person$Indirect<- sample(0:1, 1, replace=T,prob=c(1-parameters$indirect2,1-parameters$indirect2))
    person$Susp<-  round(person$Crim +   rnorm(1,1,1))
      if(person$Susp<0)
  {person$Susp<-0}
}
person$DirectCode<-paste0(person$Group,'.',person$Susp)
  population<-rbind(population,person)
  person$IndirectCode<-paste0(person$Indirect,'.',person$Susp)
  population<-rbind(population,person)
}
return(population)
}

```
################################################
## Function Policywork
################################################
```{r}
policywork<-function(policytest,test)
{
policytest<- data.frame(unlist(policytest))
policytest<-cbind(policytest,State=rownames(policytest))
policytest$State<-as.character(policytest$State)
     finalpolicy<-NA
for (ii in 1:nrow(policytest))
{
 policytest$State[ii]<-sub('X','', policytest$State[ii])
}
finalpolicy<-data.frame("State"=NA,"Action"=NA, "Reward"=NA, "LeftCrim"=NA, "LeftGroup"=NA, "LeftSusp"=NA, "LeftReward"=NA, "RightCrim"=NA, "RightGroup"=NA, "RightSusp"=NA, "RightReward"=NA, "NextState"=NA)
finalpolicy2<-finalpolicy

 for(jj in 1:nrow(test))
 {
   for (kk in 1:nrow(policytest))
{

   if(policytest$State[kk]==test$State[jj]&&as.character(policytest$unlist.policytest.[kk])==as.character(test$Action[jj]))
    { finalpolicy2$State<-policytest$State[kk]
   finalpolicy2$Action<-policytest$unlist.policytest.[kk]
   finalpolicy2$Reward<-test$Reward[jj]
   finalpolicy2$LeftCrim<-test$LeftCrim[jj]   
      finalpolicy2$LeftGroup<-test$LeftGroup[jj]  
         finalpolicy2$LeftSusp<-test$LeftSusp[jj] 
         finalpolicy2$LeftReward<-test$LeftReward[jj]    
                           finalpolicy2$RightCrim<-test$RightCrim[jj] 
                  finalpolicy2$RightGroup<-test$RightGroup[jj]  
         finalpolicy2$RightSusp<-test$RightSusp[jj] 
         finalpolicy2$RightReward<-test$RightReward[jj]          
            finalpolicy2$NextState<-test$NextState[jj] 
   finalpolicy<-rbind(finalpolicy, finalpolicy2)
 }
   }
   }
finalpolicy<-unique(finalpolicy)
finalpolicy<-na.omit(finalpolicy)
return(finalpolicy)
}
```
################################################
##This is a routine to find the best soultion
################################################
```{r}
RLSolution<-function(finalpolicy)
{
  print("A")
RLsolution<-finalpolicy[1,]
for(ii in 1:parameters$daylength)
{
  if(!is.na(RLsolution$NextState[ii]))
  {
  if(RLsolution$NextState[ii]=="End")
  {break}
  for(jj in 1:nrow(finalpolicy))
{
if (RLsolution$NextState[ii]==finalpolicy$State[jj])
   {
   RLsolution[ii+1,]<-finalpolicy[jj,]
}
}
}
for(kk in 1:nrow(RLsolution))
{if (RLsolution$Action[kk]=="Left")
{RLsolution$Group[kk]<-RLsolution$LeftGroup[kk]}
if (RLsolution$Action[kk]=="Right")  
{RLsolution$Group[kk]<-RLsolution$RightGroup[kk]}
  if (RLsolution$Action[kk]=="None")  
{RLsolution$Group[kk]<-NA}
 } }
return(RLsolution)
}
```
################################################
##
################################################

```{r}
library(stringi)
library(dplyr)
library(ReinforcementLearning)
library(binaryLogic)
library(stats)
library(hash)
library(ggplot2)
library(testthat)
library(wesanderson)
#setwd("~/Alethea")

parameters<-LoadParameters()

population<-createpopulation(parameters)
test_rand<-sample.int(n = nrow(population), size = 666, replace = F)
trainpopulation <- population[test_rand, ]
testpopulation <- population[-test_rand, ]

save(testpopulation, file = paste0("TestPopulation.",parameters$seed,".rda"))
save(trainpopulation, file = paste0("TrainPopulation.",parameters$seed,".rda"))
write.csv(trainpopulation, file = paste0("TrainPopulation.",parameters$seed,".csv"),row.names=FALSE)
write.csv(testpopulation, file = paste0("TestPopulation.",parameters$seed,".csv"),row.names=FALSE)

createsample<-createsamplefunction(trainpopulation, parameters)
createsampleSusp<-createsample
createsampleDirect<-createsample
createsampleIndirect<-createsample
createsampleCrim<-createsample
createsampleRandom<-createsample
```
################################################
##
################################################
```{r}
for(i in 1:nrow(createsample))
{
createsampleSusp$State[i]<-createsample$SuspState[i]
createsampleSusp$NextState[i]<-createsample$SuspNextState[i]

createsampleDirect$State[i]<-createsample$DirectState[i]
createsampleDirect$NextState[i]<-createsample$DirectNextState[i]

createsampleIndirect$State[i]<-createsample$IndirectState[i]
createsampleIndirect$NextState[i]<-createsample$IndirectNextState[i]

createsampleCrim$State[i]<-createsample$CrimState[i]
createsampleCrim$NextState[i]<-createsample$CrimNextState[i]

createsampleRandom$State[i]<-createsample$RandomState[i]
createsampleRandom$NextState[i]<-createsample$RandomNextState[i]
}

trainSusp<-statediagramfunction(createsampleSusp, parameters)
trainmodelSusp<-runRLinit(trainSusp, parameters)

trainDirect<-statediagramfunction(createsampleDirect, parameters)
trainmodelDirect<-runRLinit(trainDirect, parameters)

trainIndirect<-statediagramfunction(createsampleIndirect, parameters)
trainmodelIndirect<-runRLinit(trainIndirect, parameters)

trainCrim<-statediagramfunction(createsampleCrim, parameters)
trainmodelCrim<-runRLinit(trainCrim, parameters)

trainRandom<-statediagramfunction(createsampleRandom, parameters)
trainmodelRandom<-runRLinit(trainRandom, parameters)

for (m in 1:parameters$numtrain)
{

RLtrainsample<-createsamplefunction(trainpopulation, parameters)
RLtrainsampleSusp<-RLtrainsample
RLtrainsampleDirect<-RLtrainsample
RLtrainsampleIndirect<-RLtrainsample
RLtrainsampleCrim<-RLtrainsample
RLtrainsampleRandom<-RLtrainsample
for(i in 1:parameters$daylength)
{

RLtrainsampleSusp$State[i]<-as.character(RLtrainsample$SuspState[i])
RLtrainsampleSusp$NextState[i]<-as.character(RLtrainsample$NextSuspState[i])

RLtrainsampleDirect$State[i]<-as.character(RLtrainsample$DirectState[i])
RLtrainsampleDirect$NextState[i]<-as.character(RLtrainsample$NextDirectState[i])

RLtrainsampleIndirect$State[i]<-as.character(RLtrainsample$IndirectState[i]) 
RLtrainsampleIndirect$NextState[i]<-as.character(RLtrainsample$NextIndirectState[i])

RLtrainsampleCrim$State[i]<-as.character(RLtrainsample$CrimState[i])
RLtrainsampleCrim$NextState[i]<-as.character(RLtrainsample$NextCrimState[i])

RLtrainsampleRandom$State[i]<-as.character(RLtrainsample$RandomState[i])
RLtrainsampleRandom$NextState[i]<-as.character(RLtrainsample$NextRandomState[i])

}
trainSusp<-statediagramfunction(RLtrainsampleSusp, parameters)
trainmodelSusp<-runRL(trainSusp, trainmodelSusp,parameters)
policytrainSusp<-computePolicy(trainmodelSusp)

RLsolutionTrainSusp2<-RLSolution(policytrainSusp)

RLtableTrainSusp2<-as.data.frame(table(RLsolutionTrainSusp2$Group))
proportionTrainSusp2<-RLtableTrainSusp2[2,2]/(RLtableTrainSusp2[1,2]+RLtableTrainSusp2[2,2])

RLsolutionTrainSusp<-rbind(RLsolutionTrainSusp,RLsolutionTrainSusp2)
RLtableTrainSusp<-rbind(RLtableTrainSusp,RLtableTrainSusp2)
proportionTrainSusp<-rbind(proportionTrainSusp,proportionTrainSusp2)

trainDirect<-statediagramfunction(RLtrainsampleDirect, parameters)
trainmodelDirect<-runRL(trainDirect, trainmodelDirect,parameters)
policytrainDirect<-computePolicy(trainmodelDirect)

RLsolutionTrainDirect2<-RLSolution(policytrainDirect)
RLtableTrainDirect2<-as.data.frame(table(RLsolutionTrainDirect2$Group))
proportionTrainDirect2<-RLtableTrainDirect2[2,2]/(RLtableTrainDirect2[1,2]+RLtableTrainDirect2[2,2])

RLsolutionTrainDirect<-rbind(RLsolutionTrainDirect,RLsolutionTrainDirect2)
RLtableTrainDirect<-rbind(RLtableTrainDirect,RLtableTrainDirect2)
proportionTrainDirect<-rbind(proportionTrainDirect,proportionTrainDirect2)

trainIndirect<-statediagramfunction(RLtrainsampleIndirect, parameters)
trainmodelIndirect<-runRL(trainIndirect, trainmodelIndirect,parameters)
policytrainIndirect<-computePolicy(trainmodelIndirect)

RLsolutionTrainIndirect2<-RLSolution(policytrainIndirect)
RLtableTrainIndirect2<-as.data.frame(table(RLsolutionTrainIndirect2$Group))
proportionTrainIndirect2<-RLtableTrainIndirect2[2,2]/(RLtableTrainIndirect2[1,2]+RLtableTrainIndirect2[2,2])

RLsolutionTrainIndirect<-rbind(RLsolutionTrainIndirect,RLsolutionTrainIndirect2)
RLtableTrainIndirect<-rbind(RLtableTrainIndirect,RLtableTrainIndirect2)
proportionTrainIndirect<-rbind(proportionTrainIndirect,proportionTrainIndirect2)

trainCrim<-statediagramfunction(RLtrainsampleCrim, parameters)
trainmodelCrim<-runRL(trainCrim, trainmodelCrim,parameters)
policytrainCrim<-computePolicy(trainmodelCrim)

RLsolutionTrainCrim2<-RLSolution(policytrainCrim)
RLtableTrainCrim2<-as.data.frame(table(RLsolutionTrainCrim2$Group))
proportionTrainCrim2<-RLtableTrainCrim2[2,2]/(RLtableTrainCrim2[1,2]+RLtableTrainCrim2[2,2])

RLsolutionTrainCrim<-rbind(RLsolutionTrainCrim,RLsolutionTrainCrim2)
RLtableTrainCrim<-rbind(RLtableTrainCrim,RLtableTrainCrim2)
proportionTrainCrim<-rbind(proportionTrainCrim,proportionTrainCrim2)

trainRandom<-statediagramfunction(RLtrainsampleRandom, parameters)
trainmodelRandom<-runRL(trainRandom, trainmodelRandom,parameters)
policytrainRandom<-computePolicy(trainmodelRandom)

policyTrainRandom<-policywork(policytrainRandom,trainRandom)
RLsolutionTrainRandom2<-RLSolution(policyTrainRandom)
RLtableTrainRandom2<-as.data.frame(table(RLsolutionTrainRandom2$Group))
proportionTrainRandom2<-RLtableTrainRandom2[2,2]/(RLtableTrainRandom2[1,2]+RLtableTrainRandom2[2,2])

RLsolutionTrainRandom<-rbind(RLsolutionTrainRandom,RLsolutionTrainRandom2)
RLtableTrainRandom<-rbind(RLtableTrainRandom,RLtableTrainRandom2)
proportionTrainRandom<-rbind(proportionTrainRandom,proportionTrainRandom2)
}
RLtableTrainSusp <- na.omit(RLtableTrainSusp)
RLtableTrainDirect <- na.omit(RLtableTrainDirect)
RLtableTrainIndirect <- na.omit(RLtableTrainIndirect)
RLtableTrainCrim <- na.omit(RLtableTrainCrim)
RLtableTrainRandom <- na.omit(RLtableTrainRandom)

proportionTrainSusp <- na.omit(proportionTrainSusp)
proportionTrainDirect <- na.omit(proportionTrainDirect)
proportionTrainIndirect <- na.omit(proportionTrainIndirect)
proportionTrainCrim <- na.omit(proportionTrainCrim)
proportionTrainRandom <- na.omit(proportionTrainRandom)

proportionTrainDF<-cbind(proportionTrainSusp,proportionTrainDirect,proportionTrainIndirect,proportionTrainCrim,proportionTrainRandom)
names(proportionTrainDF) <- c("Suspicious", "Direct","Indirect","Criminal","Random")

boxplot(proportionTrainDF)

```
################################################
##
################################################
```{r}
RLsolutionSusp<-NA
RLsolutionDirect<-NA
RLsolutionIndirect<-NA
RLsolutionCrim<-NA
RLsolutionRandom<-NA

RLtableSusp<-NA
RLtableDirect<-NA
RLtableIndirect<-NA
RLtableCrim<-NA
RLtableRandom<-NA

proportionSusp<-NA
proportionDirect<-NA
proportionIndirect<-NA
proportionCrim<-NA
proportionRandom<-NA


for(j in 1:parameters$numtest)
{
RLtestsample<-createsamplefunction(testpopulation, parameters)
RLtestsampleSusp<-RLtestsample
RLtestsampleDirect<-RLtestsample
RLtestsampleIndirect<-RLtestsample
RLtestsampleCrim<-RLtestsample
RLtestsampleRandom<-RLtestsample

for(i in 1:nrow(RLtrainsample))
{
RLtestsampleSusp$State[i]<-as.character(RLtestsample$SuspState[i])
RLtestsampleSusp$NextState[i]<-as.character(RLtestsample$NextSuspState[i])

RLtestsampleDirect$State[i]<-as.character(RLtestsample$DirectState[i])
RLtestsampleDirect$NextState[i]<-as.character(RLtestsample$NextDirectState[i])

RLtestsampleIndirect$State[i]<-as.character(RLtestsample$IndirectState[i]) 
RLtestsampleIndirect$NextState[i]<-as.character(RLtestsample$NextIndirectState[i])

RLtestsampleCrim$State[i]<-as.character(RLtestsample$CrimState[i])
RLtestsampleCrim$NextState[i]<-as.character(RLtestsample$NextCrimState[i])

RLtestsampleRandom$State[i]<-as.character(RLtestsample$RandomState[i])
RLtestsampleRandom$NextState[i]<-as.character(RLtestsample$NextRandomState[i])
}

testSusp<-statediagramfunction(RLtestsampleSusp, parameters)
testmodelSusp<-runRL(testSusp,trainmodelSusp,parameters)

testDirect<-statediagramfunction(RLtestsampleDirect, parameters)
testmodelDirect<-runRL(testDirect,trainmodelDirect,parameters)

testIndirect<-statediagramfunction(RLtestsampleIndirect, parameters)
testmodelIndirect<-runRL(testIndirect,trainmodelIndirect,parameters)

testCrim<-statediagramfunction(RLtestsampleCrim, parameters)
testmodelCrim<-runRLinit(testCrim,parameters)

testRandom<-statediagramfunction(RLtestsampleRandom, parameters)
testmodelRandom<-runRLinit(testRandom,parameters)

policytestSusp<-computePolicy(testmodelSusp)
finalpolicySusp<-policywork(policytestSusp,testSusp)
RLsolutionSusp2<-RLSolution(finalpolicySusp)
RLtableSusp2<-as.data.frame(table(RLsolutionSusp2$Group))
proportionSusp2<-RLtableSusp2[2,2]/(RLtableSusp2[1,2]+RLtableSusp2[2,2])

RLsolutionSusp<-rbind(RLsolutionSusp,RLsolutionSusp2)
RLtableSusp<-rbind(RLtableSusp,RLtableSusp2)
proportionSusp<-rbind(proportionSusp,proportionSusp2)

policytestDirect<-computePolicy(testmodelDirect)
finalpolicyDirect<-policywork(policytestDirect,testDirect)
RLsolutionDirect2<-RLSolution(finalpolicyDirect)
RLtableDirect2<-as.data.frame(table(RLsolutionDirect2$Group))
proportionDirect2<-RLtableDirect2[2,2]/(RLtableDirect2[1,2]+RLtableDirect2[2,2])

RLsolutionDirect<-rbind(RLsolutionDirect,RLsolutionDirect2)
RLtableDirect<-rbind(RLtableDirect,RLtableDirect2)
proportionDirect<-rbind(proportionDirect,proportionDirect2)

policytestIndirect<-computePolicy(testmodelIndirect)
finalpolicyIndirect<-policywork(policytestIndirect, testIndirect)
RLsolutionIndirect2<-RLSolution(finalpolicyIndirect)
RLtableIndirect2<-as.data.frame(table(RLsolutionIndirect2$Group))
proportionIndirect2<-RLtableIndirect2[2,2]/(RLtableIndirect2[1,2]+RLtableIndirect2[2,2])

RLsolutionIndirect<-rbind(RLsolutionIndirect,RLsolutionIndirect2)
RLtableIndirect<-rbind(RLtableIndirect,RLtableIndirect2)
proportionIndirect<-rbind(proportionIndirect,proportionIndirect2)

policytestCrim<-computePolicy(testmodelCrim)
finalpolicyCrim<-policywork(policytestCrim,testCrim)
RLsolutionCrim2<-RLSolution(finalpolicyCrim)
RLtableCrim2<-as.data.frame(table(RLsolutionCrim2$Group))
proportionCrim2<-RLtableCrim2[2,2]/(RLtableCrim2[1,2]+RLtableCrim2[2,2])

RLsolutionCrim<-rbind(RLsolutionCrim,RLsolutionCrim2)
RLtableCrim<-rbind(RLtableCrim,RLtableCrim2)
proportionCrim<-rbind(proportionCrim,proportionCrim2)

policytestRandom<-computePolicy(testmodelRandom)
finalpolicyRandom<-policywork(policytestRandom,testRandom)
RLsolutionRandom2<-RLSolution(finalpolicyRandom)
RLtableRandom2<-as.data.frame(table(RLsolutionRandom2$Group))
proportionRandom2<-RLtableRandom2[2,2]/(RLtableRandom2[1,2]+RLtableRandom2[2,2])

RLsolutionRandom<-rbind(RLsolutionRandom,RLsolutionRandom2)
RLtableRandom<-rbind(RLtableRandom,RLtableRandom2)
proportionRandom<-rbind(proportionRandom,proportionRandom2)
}
RLtableSusp <- na.omit(RLtableSusp)
RLtableDirect <- na.omit(RLtableDirect)
RLtableIndirect <- na.omit(RLtableIndirect)
RLtableCrim <- na.omit(RLtableCrim)
RLtableRandom <- na.omit(RLtableRandom)

proportionSusp <- na.omit(proportionSusp)
proportionDirect <- na.omit(proportionDirect)
proportionIndirect <- na.omit(proportionIndirect)
proportionCrim <- na.omit(proportionCrim)
proportionRandom <- na.omit(proportionRandom)

proportionDF<-cbind(proportionSusp,proportionDirect,proportionIndirect,proportionCrim,proportionRandom)
names(proportionDF) <- c("Suspicious", "Direct","Indirect","Criminal","Random")

boxplot(proportionDF)
print("Suspicion")
table(RLsolutionSusp$Group)
save(RLsolutionSusp, file = paste0("RLsolutionSusp.daylength.",parameters$daylength,".numtrain.",parameters$numtrain,".numtest.",parameters$numtest,".itertrain.",parameters$itertrain,".rda"))

print("Direct")
table(RLsolutionDirect$Group)
save(RLsolutionDirect, file = paste0("RLsolutionDirect.daylength.",parameters$daylength,".numtrain.",parameters$numtrain,".numtest.",parameters$numtest,".itertrain.",parameters$itertrain,".rda"))

print("Indirect")
table(RLsolutionIndirect$Group)
save(RLsolutionIndirect, file = paste0("RLsolutionIndirect.daylength.",parameters$daylength,".numtrain.",parameters$numtrain,".numtest.",parameters$numtest,".itertrain.",parameters$itertrain,".rda"))

print("Criminal")
table(RLsolutionCrim$Group)
save(RLsolutionCrim, file = paste0("RLsolutionCrim.daylength.",parameters$daylength,".numtrain.",parameters$numtrain,".numtest.",parameters$numtest,".itertrain.",parameters$itertrain,".rda"))

print("Random")
table(RLsolutionRandom$Group)
save(RLsolutionRandom, file = paste0("RLsolutionRandom.daylength.",parameters$daylength,".numtrain.",parameters$numtrain,".numtest.",parameters$numtest,".itertrain.",parameters$itertrain,".rda"))

```
################################################
##
################################################
```{r}
testmodelIdealSusp<-runRLinit(testSusp,parameters)
policytestIdealSusp<-computePolicy(testmodelIdealSusp)
finalpolicyIdealSusp<-policywork(policytestIdealSusp,testSusp)
RLsolutionSuspIdeal<-RLSolution(finalpolicyIdealSusp)
table(RLsolutionSuspIdeal$Group)
save(RLsolutionSuspIdeal, file = paste0("RLsolutionSuspIdeal.itertrain.",parameters$itertrain,".rda"))

testmodelIdealDirect<-runRLinit(testDirect,parameters)
policytestIdealDirect<-computePolicy(testmodelIdealDirect)
finalpolicyIdealDirect<-policywork(policytestIdealDirect,testDirect)
RLsolutionDirectIdeal<-RLSolution(finalpolicyIdealDirect)
table(RLsolutionDirectIdeal$Group)
save(RLsolutionDirectIdeal, file = paste0("RLsolutionDirectIdeal.itertrain.",parameters$itertrain,".rda"))

testmodelIdealIndirect<-runRLinit(testIndirect,parameters)
policytestIdealIndirect<-computePolicy(testmodelIdealIndirect)
finalpolicyIdealIndirect<-policywork(policytestIdealIndirect, testIndirect)
RLsolutionIndirectIdeal<-RLSolution(finalpolicyIdealIndirect)
table(RLsolutionIndirectIdeal$Group)
save(RLsolutionIndirect, file = paste0("RLsolutionIndirectIdeal.itertrain.",parameters$itertrain,".rda"))

testmodelIdealCrim<-runRLinit(testCrim,parameters)
policytestIdealCrim<-computePolicy(testmodelIdealCrim)
finalpolicyIdealCrim<-policywork(policytestIdealCrim,testCrim)
RLsolutionCrimIdeal<-RLSolution(finalpolicyIdealCrim)
table(RLsolutionCrimIdeal$Group)
save(RLsolutionCrimIdeal, file = paste0("RLsolutionCrimIdeal.itertrain.",parameters$itertrain,".rda"))

testmodelIdealRandom<-runRLinit(testRandom,parameters)
policytestIdealRandom<-computePolicy(testmodelIdealRandom)
finalpolicyIdealRandom<-policywork(policytestIdealRandom,testRandom)
RLsolutionRandomIdeal<-RLSolution(finalpolicyIdealRandom)
table(RLsolutionRandomIdeal$Group)
save(RLsolutionRandomIdeal, file = paste0("RLsolutionRandomIdeal.itertrain.",parameters$itertrain,".rda"))
save(proportionDF, file ="proportionDF.rda")

```

