---
title: "R Notebook"
output: html_notebook
---

```{r}
library(stringi)
simplepop <- read.csv("~/RLProject/Simple/simplepop.csv")
id_num<-sample(100:140, 40, replace=F)
for(i in 1: nrow(simplepop))
{
  simplepop$ID[i]<-id_num[i]
  simplepop$Code[i]<-paste0(simplepop$ID[i],'.',simplepop$Type[i],'.',simplepop$Susp[i])
}
```
```{r}
id_num0<-sample(1:40, 40, replace=F)
Left<-NA
Right<-NA
LeftCode<-NA
RightCode<-NA
LeftReward<-NA
RightReward<-NA
State<-NA
for(i in 1: nrow(simplepop)/2)
{
id_num1<-id_num0[i]
id_num2<-id_num0[i+20]
Left[i]<-id_num1
Right[i]<-id_num2
LeftCode[i]<-simplepop$Code[id_num1]
RightCode[i]<-simplepop$Code[id_num2]
LeftReward[i]<-simplepop$Crim[id_num1]
RightReward[i]<-simplepop$Crim[id_num2]
State[i]<-paste0(LeftCode[i],'.',RightCode[i])
}
createmap<-data.frame(Left, Right,LeftCode, RightCode, LeftReward, RightReward, State)
View(createmap)
 write.csv(createmap, file = "createmap.csv",row.names=FALSE)
```

```{r}
time = 24
detain = 3
move = 1
statemap<-data.frame("State"=paste0(time,".",createmap$State[1]), "Action"="Left", "Reward"=createmap$LeftReward[1], "NextState"=paste0(time-detain,".",createmap$State[2]))
nextrow<-data.frame("State"=paste0(time,".",createmap$State[1]), "Action"="Right", "Reward"=createmap$RightReward[1], "NextState"=paste0(time-detain,".",createmap$State[2]))
statemap<-rbind(statemap,nextrow)
nextrow<-data.frame("State"=paste0(time,".",createmap$State[1]), "Action"="None", "Reward"=0, "NextState"=paste0(time-move,".",createmap$State[2]))
statemap<-rbind(statemap,nextrow)
```

```{r}
lefttime<-unlist(strsplit(as.character(statemap$NextState[1]),".", fixed = TRUE))
newlefttime<-lefttime[7]

statemap2<-data.frame("State"=paste0(statemap$NextState[1]), "Action"="Left", "Reward"=createmap$LeftReward[1], "NextState"=paste0(createmap$State[2],".",time-detain))
nextrow<-data.frame("State"=paste0(createmap$State[1],".",time), "Action"="Right", "Reward"=createmap$RightReward[1], "NextState"=paste0(createmap$State[2],".",time-detain))
statemap<-rbind(statemap,nextrow)
nextrow<-data.frame("State"=paste0(createmap$State[1],".",time), "Action"="None", "Reward"=0, "NextState"=paste0(createmap$State[2],".",time-move))
statemap<-rbind(statemap,nextrow)

```

```{r}
for(i in 1:time)
{
statedummy<-statemap$NextState[i]

for(j in 1:nrow(statemap))
{
flag<-0
  if (statedummy==statemap$State[j])  {
    flag<-1
    }
}
if(flag==0)
{
openstate<-unlist(stri_split_fixed(as.character(statedummy),".", fixed = TRUE, n=2))
for (k in 1:nrow(createmap))
{
if (openstate[2]==createmap$State[k])
{print(createmap$State[k]) }
}
} 
}
```

statemapdummy<-data.frame("State"=statedummy, "Action"="Left", "Reward"=createmap$LeftReward[1], "NextState"=paste0(createmap$State[2],".",time-detain))
nextrow<-data.frame("State"=paste0(createmap$State[1],".",time), "Action"="Right", "Reward"=createmap$RightReward[1], "NextState"=paste0(createmap$State[2],".",time-detain))
statemap<-rbind(statemap,nextrow)
nextrow<-data.frame("State"=paste0(createmap$State[1],".",time), "Action"="None", "Reward"=0, "NextState"=paste0(createmap$State[2],".",time-move))