#---
#project: "Aletheia2019"
#title: InitializePopulation.Rmd
#output: html_notebook
#location: ~/Documents/Research/Aletheia2019

#university: University of Colorado at Denver
#class: MATH 6388
#professor: Audrey Hendricks

#author: Kathleen Gatliffe
#date: 25 January 15
#---

# This file creates the population data file for the Aletheia2019 project.

```{r}
#setwd("/Users/gatliffe/Documents/Research/Aletheia2019")
library(binaryLogic)
library(stats)
library(dplyr)
library(hash)
library(ggplot2)
library(ReinforcementLearning)
library(testthat)
library(wesanderson)
```

# Load function file, parameters, color palettes.

```{r}
#source("AllKFunctions.R")
source("Parameters.R")
#source("AllKPalettes.R")
```

# Load parameters.

```{r}
Parameters<-LoadParameters()
```

# This is the population seeding routine.

```{r}

set.seed=(Parameters$seed)

Population = data.frame(matrix(vector(), 0, 11, dimnames=list(c(), c("ID", "Type","Target", "Random", "Indirect","ClueNoInfo", "ClueType", "ClueIndirect", "TimesOnMap","IgnoreHistory", "DetainHistory" ))),stringsAsFactors=F)
Person = data.frame(matrix(vector(), 1, 11, dimnames=list(c(), c("ID", "Type","Target", "Random", "Indirect","ClueNoInfo", "ClueType", "ClueIndirect","TimesOnMap","IgnoreHistory", "DetainHistory"))),stringsAsFactors=F)
for (i in 1:Parameters$pop)
{
Person$ID <-sprintf("%03d",i)
Person$Type <- sample(0:1, 1, replace=T,prob=c(1-Parameters$perctype,Parameters$perctype))
Person$Target <- sample(0:1, 1, replace=T,prob=c(1-Parameters$perctarget,Parameters$perctarget))
Person$Random<- sample(0:5, 1, replace=T)
if (Person$Type==0)
  {Person$Indirect<- sample(0:1, 1, replace=T,prob=c(1-Parameters$indirect0,Parameters$indirect0))}
if (Person$Type==1)
{Person$Indirect<- sample(0:1, 1, replace=T,prob=c(1-Parameters$indirect1,1-Parameters$indirect1))}
  Person$ClueNoInfo <-3*Person$Target+Person$Random
  Person$ClueType <-3*Person$Target+Person$Type+Person$Random
  Person$ClueIndirect <-3*Person$Target+Person$Indirect+Person$Random  
  Person$TimesOnMap<-0
  Person$IgnoreHistory<-0
  Person$DetainHistory<-0
  Population<-rbind(Population,Person)
}

save(Population, file = paste0("Population.",Parameters$seed,".rda"))
write.csv(Population, file = paste0("Population.",Parameters$seed,".csv"),row.names=FALSE)
```

# Reweighting Suspicious. This chunk creates a version of population where the only 
#change is that type 2 is rated more suspicious.

#```{r}
#PopulationY<-PopulationN
#  for (j in 1:Parameters$pop)
#{
#    if (PopulationY$Type[j]=="2")
#PopulationY$Suspicious[j] <- PopulationY$Suspicious[j]*(1+Parameters$bias)
#    Person$SuspWeight <- 0
#PopulationY$SuspTot <-PopulationY$Suspicious+PopulationY$SuspWeight
#roundedsusp<-round(PopulationY$SuspTot*100)
#PopulationY$DetainState<-sprintf("%03d",roundedsusp)
#  }

#save(PopulationY, file = paste0("/Users/gatliffe/Documents/In Process/ASM Final Project/Aletheia/Iteration/PopulationY.",Parameters$seed,".", Parameters$bias,".rda"))
#write.csv(PopulationY, file = paste0("/Users/gatliffe/Documents/In Process/ASM Final Project/Aletheia/Iteration/PopulationY.",Parameters$seed,".", Parameters$bias,".csv"),row.names=FALSE)
#```
